%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}



\name{George Corney} % Your name
\address{163 Pinnocks Way \\ Oxford \\ OX2 9DF} % Your address
\address{07542 045079 \\ \href{mailto:haxiomic@gmail.com}{haxiomic@gmail.com}} % Your phone number and email

\begin{document}


\begin{rSection}{Introduction}
% Creative Technologist
\item Previous clients include Microsoft, LG, Atlantic Productions and the Met Office. My work both personal and contracted has reached millions of users and featured on sites like \href{http://thenextweb.com/creativity/2015/05/15/webgl-fluid-experiment-is-a-browser-based-lsd-trip/}{The Next Web}, \href{http://www.gizmodo.co.uk/2014/11/just-try-and-stop-playing-with-this-fluid-simulator/}{Gizmodo} and \href{http://www.fastcodesign.com/3038725/this-wonderful-web-toy-turns-your-browser-into-magic-liquid}{FastCoDesign}.

\item I specialize in web development and computer graphics, however, I'm never shy to grapple with a new domain to meet the demands of a project.

\item I'm an advocate of open source and you can find my contributions under the handle \href{http://github.com/haxiomic}{`haxiomic'}.

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Microsoft}{June 2016 - August 2017}{WebGL, GLSL, Physically Based Rendering, C++}{Contracting}
\item Working on Microsoft's internal cross-platform physically-based rendering engine used in products including Office, Windows 10 shell and Paint3D.
\item I developed the PBR pipeline for the WebGL version of the engine and much of my work on the WebGL engine is now available in \href{https://www.babylonjs.com/demos/pbrglossy/}{BablyonJS}.
\item During this time also I worked on optimizing rendering and launch performance in MS Paint's successor, Paint3D.
\end{rSubsection}

\begin{rSubsection}{Alchemy VR}{Feb 2016 - June 2016}{VR, C++, three.js, WebGL, GLSL, node.js}{Contracting}
\item \href{http://www.alchemyvr.com/}{Alchemy VR} are transitioning to distributing their VR films directly to users (rather then through exhibitions), I was contracted to develop the cross-platform Netflix-style video store to enable this.
\item To provide a cross-platform base (where bundling a webview wasn't an option) I implemented the WebGL API over GLES using the V8 JavaScript engine (C++), this enabled us to reap the benefits of developing for the web (live feedback, easy distribution, easier to hire developers etc), whilst allowing access to native code and APIs where necessary.
\item I was also responsible for developing the media delivery systems, which involved writing a content delivery server in node.js and developing an in-house DRM system.
\end{rSubsection}

\begin{rSubsection}{Atlantic Productions}{Dec 2015 - Feb 2016}{three.js, WebGL, GLSL, HTML, SCSS}{Contracting}
\item Contracted to develop interactive features for a companion website to \href{http://www.atlanticproductions.tv/}{Atlantic Productions} recent series ``David Attenbrough's Great Barrier Reef''. Features included a \href{http://attenboroughsreef.com/_mobile/interactive_weather_globe.php}{WebGL globe displaying animated wind flow, atmospheric temperature and ocean current data}
\end{rSubsection}

\begin{rSubsection}{DinahMoe}{Nov 2015}{WebGL, GLSL, three.js, Front-end Web}{Contracting}
\item Contracted by \href{http://dinahmoe.com/}{DinahMoe} to develop portions of an interactive WebGL film, Canada Goose's ``Out There''. The project included developing a system to render WebGL output to video.
\end{rSubsection}

\begin{rSubsection}{LG \& Responsive Ads}{Sept 2015}{WebGL, GLSL, Front-end Web}{Contracting}
\item As part of an \href{http://www.lg.com/uk/oled-tv}{LG OLED TV} ad campaign, I was contracted to produce an interactive WebGL fluid and particle simulation in collaboration with \href{http://www.responsiveads.com/}{responsiveads}.
\item The ad was required to run smoothly in all modern browsers, including mobiles and underpowered devices. The computationally intensive nature of the simulation required heavy optimization and an adaptive quality system.
\item Traditionally this sort of simulation requires extensions to WebGL (such as floating point textures), to enable maximum compatibility, techniques were developed to pack simulation data into 4 byte textures which were available in every WebGL instance (whereas extensions are not).
\item A early preview version of the ad is \href{http://haxiomic.github.io/ig783wghhnod/new-brush/}{available}.
\end{rSubsection}

\begin{rSubsection}{Met Office}{June 2015}{WebGL, GLSL}{Consulting}
\item The \href{http://www.informaticslab.co.uk/}{Met Office Informatics Lab} were developing a browser-based 3D visualization of live weather in the UK. I was brought in to consult on techniques for high-performance volumetric rendering and approaches to resolve performance issues their initial WebGL ray marching implementation.
\end{rSubsection}

\begin{rSubsection}{Alchemy VR}{June 2015, Sept 2015}{Java, C++, Android, Mobile}{Contracting}
\item \href{http://www.alchemyvr.com/}{Alchemy VR} is a recently formed branch of \href{http://www.atlanticproductions.tv/}{Atlantic Productions}, their VR premier ``David Attenborough's First Life'' was to be shown on 80 Gear VRs in the Natural History Museum from the 12th of June (2015).
\item Alchemy asked me to solve a number of critical problems two weeks before their premier deadline. I was tasked with developing a custom VR video player and bypassing the built-in Oculus Home without resorting to rooting the devices.
\item The custom VR video player was developed using C++, Java Native Interface and Oculus's Mobile SDK and the bypass was developed with Java and the Android API.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{fffunction}{Apr 2015}{JavaScript, backbone.js, HTML, SCSS}{Contracting}
\item \href{http://fffunction.co/}{fffunciton} is a digial design agency in the Southwest with clients that include \href{http://www.roland.co.uk}{Roland UK} and the Bristol museums group (\href{http://bristolmuseums.org.uk}{BMGA}).
\item I was brought in to contribute to a browser-based book reader and preview app (commissioned by Oxford University Press). The app was developed with backbone.js, node.js and Grunt. 
\item My role involved developing a page layout engine and viewer thumbnail alongside bug fixes.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Hive}{Nov 2013 - Jul 2014}{Objective-C, OS X Reverse Engineering,  UI \& UX, JavaScript}{Startup}
\item Hive was a team collaboration app I worked on with a small group during university. It was an experiment in developing the ideal collaboration tool. The philosophy was that team cohesion could be improved by reducing boundaries between computers; the goal was to be able to push content (including running programs) from one device to a teammate's immediately and intuitively (in a similar manner to moving windows between multiple displays).
\item The project won the Cisco Open Collaboration Challenge and was accelerated for 3 months at \href{http://www.dotforge.com/}{dotforge}.
\item My role in the project was development of `State-sharing' (which involved reverse engineering OS X's state saving feature), UI \& UX design, and the development of the native OS X app.
\item I left the project after the release of OS X Yosemite which contained features (Continuity and Handoff) which competed with our core technology `State-sharing'.
\end{rSubsection}

%%%% END Experience

\end{rSection}



%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Open Source Projects}

\begin{rSubsection}{WebGL Fluid}{September 2014}{GLSL, Haxe, Lime, JavaScript, C++, WebGL}{}
\item \href{https://github.com/haxiomic/GPU-Fluid-Experiments}{This project} is a GPU fluid and particle simulation written in Haxe and GLSL, targeting HTML5 for browsers and C++ for desktop and iOS. The simulation solves the Navier-Stokes equation for incompressible flow over a grid with the Jacobi method and uses the velocity field to advect over 1 million particles.
\item The motivation for this project was to explore using WebGL for high performance physics simulations and to investigate the performance factors involved.
\item It's been played with approximately \textbf{2 million times} by \textbf{1.6 million users}, achieving a total of \textbf{8 million} pageviews.
\item It has reached the front page of \href{https://www.reddit.com/r/InternetIsBeautiful/comments/2gkunq/fluid_and_particles_in_webgl/}{Reddit} (\href{https://www.reddit.com/r/InternetIsBeautiful/comments/35s6hg/in_browser_physics_simulator_xpost_pc_master_race/}{twice}) and featured in articles on
\begin{itemize}
	\item \href{http://www.fastcodesign.com/3038725/this-wonderful-web-toy-turns-your-browser-into-magic-liquid}{FastCoDesign}
	\item \href{http://thenextweb.com/creativity/2015/05/15/webgl-fluid-experiment-is-a-browser-based-lsd-trip/}{The Next Web}
	\item \href{http://www.gizmodo.co.uk/2014/11/just-try-and-stop-playing-with-this-fluid-simulator/}{Gizmodo}
	\item \href{http://www.engadget.com/2015/05/15/GPU-physics-trippy-simulation/}{engadget}
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{GLSL Parser in Haxe}{Mar 2015 - Present}{GLSL, Haxe, JavaScript, C, Context Free Grammars, LALR}{Work in Progress}
\item The aim of this project is to provide a cross-platform GLSL parser (and parser generator) that supports the GLSL reference language grammar.
\item The motivation for the development was to enable compile-time transformations (such as minification or transpilation) of GLSL source, as well as tighter integration with the host codebase when working with the Haxe compiler.
\item The project can be accessed and tested on github \href{https://github.com/haxiomic/haxe-glsl-parser}{github.com/haxiomic/haxe-glsl-parser}.
\end{rSubsection}
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Sheffield} 
%\hfill {\em June 2004}
\\
B.Sc in Physics with Astrophysics $\diamond{}$ \textit{First Class}
\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & JavaScript, GLSL, C++, C, Objective-C, Haxe, Bash \\
Technologies \& APIs & HMTL5, WebGL, Git \\
Platforms & Android, iOS, OS X, Linux  \\
Skills & UI \& UX design, Reverse Engineering \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Awards
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards}

\begin{rSubsectionSimple}{BAFTA - Best Digital Creativity - David Attenborough’s Great Barrier Reef Dive (Atlantic Productions)}{February 2017}{Android, Oculus, VR}{}
\end{rSubsectionSimple}

\begin{rSubsectionSimple}{Sudo Challenge VR/AR hackathon 1st place}{November 2017}{WebGL, pixi.js, medical technology}{}
\end{rSubsectionSimple}

\end{rSection}


\end{document}
